Estimating individual subjective values of emotion regulation strategies

### 2023-04-20 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography\newline\indent Word count: 9432}
\usepackage{lineno}

@@

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
For more detailed information on psychometric properties of the questionnaires, please see the supplementary material.

@@

The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/d6sc9/}{osf.io/d6sc9/}.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography}
\usepackage{lineno}

@@

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
Habitual use of ER was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
For more detailed information on psychometric properties of the questionnaires, please see the supplementary material.

@@

The Stage 1 Registered Report protocol has been approved and is available at \url{https://osf.io/fn9bt}.
